%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy CV/Resume
% XeLaTeX Template
% Version 1.0 (5/5/2014)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Debarghya Das (http://www.debarghyadas.com)
% With extensive modifications by:
% Vel (vel@latextemplates.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important notes:
% This template needs to be compiled with XeLaTeX.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[letterpaper]{deedy-resume} % Use US Letter paper, change to a4paper for A4 

\begin{document}

%----------------------------------------------------------------------------------------
%	TITLE SECTION
%----------------------------------------------------------------------------------------

\lastupdated % Print the Last Updated text at the top right

\namesection{Ram}{K}{ % Your name
\href{mailto:ramk.ai.engineer@gmail.com}{ramk.ai.engineer@gmail.com} | 603.858.7546 |
\href{https://www.linkedin.com/in/ram-k-aieng}{linkedin.com/in/ram} \\% Your contact information 
}

%----------------------------------------------------------------------------------------
%	LEFT COLUMN
%----------------------------------------------------------------------------------------

\begin{minipage}[t]{0.33\textwidth} % The left column takes up 33% of the text width of the page

\section{Summary}
\descript{AI Engineer building production-grade Agentic workflows, RAG pipelines, and cloud-native automation at scale.}
\sectionspace % Some whitespace after the section

%------------------------------------------------
% Education
%------------------------------------------------

\section{Education} 

\descript{Master’s in Computer Applications 2001}
\location{MK University}



\sectionspace % Some whitespace after the section

%------------------------------------------------
% Skills
%------------------------------------------------

\section*{SKILLS}
\sectionspace % Some whitespace after the section

\descript{AI \& GENAI} \\
Agentic AI, LangGraph, LangChain \\
RAG, OpenAI / Azure OpenAI \\
Prompt Engineering \\
LLM Orchestration, Evaluation \\
Guardrails, Observability \\
Embeddings, Fine-Tuning, Vector Search \\
\sectionspace % Some whitespace after the section
\descript{PYTHON FOR AI} \\
Python, FastAPI, Flask \\
NumPy, Pandas \\
FAISS, Pinecone, Chroma \\
Ray, Celery \\
Embedding Pipelines \\
\sectionspace % Some whitespace after the section
\descript{CLOUD / MLOPS} \\
AWS, GCP \\
Kubernetes, Docker \\
GitHub Actions, Jenkins \\
Model Serving, Monitoring \\
MLflow \\
\sectionspace % Some whitespace after the section
\descript{DATA} \\
PostgreSQL, MongoDB, Redis \\
Kafka, Vector Stores \\
\sectionspace % Some whitespace after the section
\descript{ARCHITECTURE} \\
LLM System Design \\
RAG Pipelines \\
Agent Workflows \\
Multi-Step Reasoning \\
Event\-Driven Systems \\
API Design \\
Inference Architecture \\



\sectionspace


\sectionspace % Some whitespace after the section
%------------------------------------------------
% Links
%------------------------------------------------

\sectionspace % Some whitespace after the section

%----------------------------------------------------------------------------------------

\end{minipage} % The end of the left column
\hfill
%
%----------------------------------------------------------------------------------------
%	RIGHT COLUMN
%----------------------------------------------------------------------------------------
%
\begin{minipage}[t]{0.66\textwidth} % The right column takes up 66% of the text width of the page

%------------------------------------------------
% Experience
%------------------------------------------------
\section{Experience}

\runsubsection{ERCOT}
\descript{| Senior AI Engineer }
\location{Apr 2025 – Present | Taylor, TX}
\begin{tightitemize}
\sectionspace
\item Built an AI-powered feasibility screening platform using Machine Learning and Flask APIs, achieving ROC-AUC > 0.85 and automating resource onboarding decisions.
\item Developed a Python-based payment monitoring solution using APScheduler and Pandas that automatically detects payment failures and generates actionable operational reports.
\item Integrated AI-driven workflows into existing enterprise systems, reducing manual analysis and improving operational efficiency.
\end{tightitemize}
\sectionspace

\runsubsection{Amazon Robotics}
\descript{| Senior AI Engineer}
\location{Feb 2023 – Mar 2025 | North Reading, MA}
\begin{tightitemize}
\item Built AI-enabled microservices supporting robotics manufacturing and warehouse automation.
\item Designed data pipelines powering ML models for predictive maintenance and robotics telemetry analytics.
\item Integrated ML inference endpoints into cloud‑native systems to automate operational decision flows.

\end{tightitemize}

\sectionspace

\runsubsection{Biogen}
\descript{| AI Solutions Engineer}
\location{Jun 2022 – Jan 2023 | Durham, NC}
\begin{tightitemize}
\item Integrated AI‑based anomaly detection into supply‑chain workflows to identify deviations in logistics and compliance events.
\item Built secure data pipelines enabling ML forecasting models for demand planning and operational risk monitoring.
\end{tightitemize}

\sectionspace

\runsubsection{Dell Technologies}
\descript{| AI Platform Architect / Application Architect }
\location{Jul 2015 – May 2022 | Austin, TX}
\begin{tightitemize}

\item Architected cloud‑native platforms supporting ML model hosting, inference APIs, and analytics pipelines.

\item Integrated recommendation engines and predictive analytics into enterprise applications.

\item Led modernization initiatives that enabled adoption of LLM‑based internal tools for search, summarization, and workflow automation.

\end{tightitemize}

\sectionspace

\runsubsection{Earlier experience}
\descript{| IBM, Innominds, and Wells Fargo}
\begin{tightitemize}
\item Delivered enterprise-scale solutions in eCommerce, financial services, PLM systems, and workflow automation using Java technologies, SOA, Spring, and web services.
\end{tightitemize}

\runsubsection{Key Achievements}
\begin{tightitemize}
\item Developed an AI-based feasibility prediction system replacing manual pre-screening processes.
\item Automated payment failure detection and reporting using Python and Machine Learning technologies.
\item Delivered enterprise cloud migrations and microservices transformations across multiple Fortune 500 organizations.
\item Achieved 99.9\% application availability through cloud-native architectures and DevOps automation.
\item Reduced deployment times by up to 60\% through CI/CD implementation and infrastructure automation.
\end{tightitemize}


%------------------------------------------------
% Awards
%------------------------------------------------

\sectionspace % Some whitespace after the section

%------------------------------------------------
% Societies
%------------------------------------------------

%\section{Membership} 

%\begin{tabular}{rll}
%2011-2015 & Alpha Kappa Lambda Fraternity\\

%\end{tabular}

%\sectionspace % Some whitespace after the section

%----------------------------------------------------------------------------------------

\end{minipage} % The end of the right column

%----------------------------------------------------------------------------------------
%	SECOND PAGE (EXAMPLE)
%----------------------------------------------------------------------------------------

%\newpage % Start a new page

%\begin{minipage}[t]{0.33\textwidth} % The left column takes up 33% of the text width of the page

%\section{Example Section}

%\end{minipage} % The end of the left column
%\hfill
%\begin{minipage}[t]{0.66\textwidth} % The right column takes up 66% of the text width of the page

%\section{Example Section 2}

%\end{minipage} % The end of the right column

%----------------------------------------------------------------------------------------

\end{document}