%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy CV/Resume
% XeLaTeX Template
% Version 1.0 (5/5/2014)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Debarghya Das (http://www.debarghyadas.com)
% With extensive modifications by:
% Vel (vel@latextemplates.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important notes:
% This template needs to be compiled with XeLaTeX.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[letterpaper]{deedy-resume} % Use US Letter paper, change to a4paper for A4 

\begin{document}

%----------------------------------------------------------------------------------------
%	TITLE SECTION
%----------------------------------------------------------------------------------------

\lastupdated % Print the Last Updated text at the top right

\namesection{Ram}{K}{ % Your name
\href{mailto:ramk.ai.engineer@gmail.com}{ramk.ai.engineer@gmail.com} | 603.858.7546 |
\href{https://www.linkedin.com/in/ram-k-aieng}{linkedin.com/in/ram} \\% Your contact information 
}

%----------------------------------------------------------------------------------------
%	LEFT COLUMN
%----------------------------------------------------------------------------------------

\begin{minipage}[t]{0.33\textwidth} % The left column takes up 33% of the text width of the page

\section{Summary}
\descript{
Senior AI Engineer with 18+ years of engineering experience, specializing in Generative AI, RAG, Agentic AI, and ML. Skilled in building enterprise AI platforms using Python, LangChain, LangGraph, LLMs, vector databases, FastAPI, and cloud technologies.}
%------------------------------------------------
% Education
%------------------------------------------------
\section{Education} 

\descript{Master of Computer Applications (MCA)}
\location{MK University}
\location{2001}

%------------------------------------------------
% Skills
%------------------------------------------------
\section{Technical Skills}

\subsection{Programming Languages}
Python \textbullet{} Java \textbullet{} SQL \textbullet{} JavaScript \textbullet{} Bash

\subsection{AI / Generative AI}
Agentic AI \textbullet{} LLMs \textbullet{} LangGraph \textbullet{} LangChain \textbullet{} RAG \textbullet{} Prompt Engineering \textbullet{} OpenAI \textbullet{} Azure OpenAI \textbullet{} Ollama

\subsection{Machine Learning}
Scikit-learn \textbullet{} Logistic Regression \textbullet{} Classification \textbullet{} Feature Engineering \textbullet{} Model Evaluation \textbullet{} ROC-AUC \textbullet{} Pandas \textbullet{} NumPy

\subsection{Vector Databases}
FAISS \textbullet{} Pinecone \textbullet{} ChromaDB \textbullet{} Embeddings \textbullet{} Vector Search

\subsection{AI Frameworks}
FastAPI \textbullet{} Flask \textbullet{} REST APIs \textbullet{} JSON \textbullet{} Pydantic

\subsection{Cloud \& MLOps}
AWS (EC2, S3, Lambda, ECS, IAM, CloudWatch) \textbullet{} Azure OpenAI \textbullet{} Docker \textbullet{} Kubernetes \textbullet{} GitHub Actions \textbullet{} Jenkins \textbullet{} MLflow

\subsection{Data Engineering}
PostgreSQL \textbullet{} MongoDB \textbullet{} Redis \textbullet{} Kafka \textbullet{} ETL Pipelines

\subsection{Architecture}
Agent Workflows \textbullet{} Multi-Agent Systems \textbullet{} LLM Orchestration \textbullet{} Inference Pipelines \textbullet{} Event-Driven Architecture \textbullet{} Microservices

\subsection{Developer Tools}
Git \textbullet{} GitHub \textbullet{} VS Code \textbullet{} Jupyter Notebook \textbullet{} Linux
\sectionspace


\sectionspace % Some whitespace after the section
%------------------------------------------------
% Links
%------------------------------------------------

\sectionspace % Some whitespace after the section

%----------------------------------------------------------------------------------------

\end{minipage} % The end of the left column
\hfill
%
%----------------------------------------------------------------------------------------
%	RIGHT COLUMN
%----------------------------------------------------------------------------------------
%
\begin{minipage}[t]{0.66\textwidth} % The right column takes up 66% of the text width of the page

%------------------------------------------------
% Experience
%------------------------------------------------
\section{Experience}

\runsubsection{ERCOT}
\descript{| Senior AI Engineer }
\location{Apr 2025 – Present | Taylor, TX}
\sectionspace
\begin{tightitemize}
\item Designed and developed enterprise AI solutions using Python, FastAPI, LangGraph, LangChain, and RAG to automate payment operations and business workflows.
\item Built multi-agent AI systems for intent classification, root cause analysis, semantic search, trend analysis, recommendations, and executive reporting.
\item Implemented Retrieval-Augmented Generation (RAG) pipelines using ChromaDB, Ollama, and local LLMs for secure enterprise knowledge retrieval.
\item Built payment monitoring and reporting solutions using Python, APScheduler, and Pandas to improve operational visibility and reduce manual effort.
\end{tightitemize}

\runsubsection{Amazon Robotics}
\descript{| Senior AI Engineer}
\location{Jun 2023 – Mar 2025 | North Reading, MA}
\begin{tightitemize}
\item Designed and developed AI-powered robotics solutions using Python, FastAPI, LangGraph, and RAG to automate warehouse operations, robot diagnostics, and predictive maintenance.
\item Built a multi-agent AI architecture for intent classification, fleet diagnostics, semantic search, predictive maintenance, task optimization, and operational reporting using LangGraph and local LLMs.
\item Developed Retrieval-Augmented Generation (RAG) pipelines using ChromaDB, Ollama, and vector embeddings to enable intelligent search and conversational AI over robotics operational data.
\end{tightitemize}


\runsubsection{Biogen}
\descript{| AI Engineer}
\location{Jun 2022 – Jun 2023 | Durham, NC}
\begin{tightitemize}
\item Integrated Llama-based Large Language Models (LLMs) with enterprise applications using FastAPI REST APIs to enable document intelligence and conversational AI.
\item Designed and implemented Retrieval-Augmented Generation (RAG) pipelines by ingesting PDF, Word, HTML, and CSV documents, generating embeddings, and indexing knowledge in ChromaDB.
\end{tightitemize}

\runsubsection{Dell Technologies}
\descript{| Machine Learning Engineer / Application Architect }
\location{Jul 2015 – May 2022 | Austin, TX}
\begin{tightitemize}
\item Designed and implemented end-to-end Machine Learning pipelines using Python, Scikit-learn, Pandas, and FastAPI for predictive analytics and automated business decision support.
\item Developed and optimized Logistic Regression models through feature engineering, model evaluation, and hyperparameter tuning to predict project feasibility with high accuracy and explainability.
\end{tightitemize}

\runsubsection{Earlier experience}
\descript{| IBM, Innominds, and Wells Fargo}
\begin{tightitemize}
\item Delivered enterprise-scale solutions in eCommerce, financial services, PLM systems, and workflow automation using Java technologies, SOA, Spring, and web services.
\end{tightitemize}

\runsubsection{Key Achievements}
\begin{tightitemize}
\item Designed and delivered enterprise AI solutions spanning Machine Learning, Generative AI, Retrieval-Augmented Generation (RAG), and Agentic AI, automating complex business workflows.
\item Built production-grade multi-agent AI platforms using LangGraph, FastAPI, ChromaDB, Ollama, and LLMs for intelligent search, root cause analysis, recommendations, and workflow automation.
\end{tightitemize}

%------------------------------------------------
% Awards
%------------------------------------------------


%------------------------------------------------
% Societies
%------------------------------------------------

%\section{Membership} 

%\begin{tabular}{rll}
%2011-2015 & Alpha Kappa Lambda Fraternity\\

%\end{tabular}

%\sectionspace % Some whitespace after the section

%----------------------------------------------------------------------------------------

\end{minipage} % The end of the right column

%----------------------------------------------------------------------------------------
%	SECOND PAGE (EXAMPLE)
%----------------------------------------------------------------------------------------

%\newpage % Start a new page

%\begin{minipage}[t]{0.33\textwidth} % The left column takes up 33% of the text width of the page

%\section{Example Section}

%\end{minipage} % The end of the left column
%\hfill
%\begin{minipage}[t]{0.66\textwidth} % The right column takes up 66% of the text width of the page

%\section{Example Section 2}

%\end{minipage} % The end of the right column

%----------------------------------------------------------------------------------------

\end{document}