%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy CV/Resume
% XeLaTeX Template
% Version 1.0 (5/5/2014)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Debarghya Das (http://www.debarghyadas.com)
% With extensive modifications by:
% Vel (vel@latextemplates.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important notes:
% This template needs to be compiled with XeLaTeX.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[letterpaper]{deedy-resume} % Use US Letter paper, change to a4paper for A4 

\begin{document}

%----------------------------------------------------------------------------------------
%	TITLE SECTION
%----------------------------------------------------------------------------------------

\lastupdated % Print the Last Updated text at the top right

\namesection{Rammohan}{Kotni}{ % Your name
\href{mailto:chrisliow@gmail.com}{ramkotni@gmail.com} | 603.858.7546 % Your contact information
}

%----------------------------------------------------------------------------------------
%	LEFT COLUMN
%----------------------------------------------------------------------------------------

\begin{minipage}[t]{0.33\textwidth} % The left column takes up 33% of the text width of the page

%------------------------------------------------
% Education
%------------------------------------------------

\section{Education} 

\descript{Master’s in Computer Applications 2001}
\location{MK University}

\sectionspace % Some whitespace after the section

\descript{Bachelor’s in Science - Mathematics }
\location{Andhra University} 



\sectionspace % Some whitespace after the section


\sectionspace % Some whitespace after the section

%------------------------------------------------
% Skills
%------------------------------------------------

\section{Technical Skills}

\subsection{Cloud}
AWS (EC2, ECS, Lambda, S3, RDS, IAM, CloudWatch) \textbullet{} Oracle Cloud (OCI)

\sectionspace

\subsection{Infrastructure as Code}
Terraform \textbullet{} CloudFormation \textbullet{} Ansible

\sectionspace

\subsection{Containers \& Orchestration}
Kubernetes \textbullet{} Docker \textbullet{} ECS \textbullet{} Fargate

\sectionspace

\subsection{CI/CD \& DevOps}
Jenkins \textbullet{} GitLab CI/CD \textbullet{} AWS CodePipeline \textbullet{} Git \textbullet{} GitHub

\sectionspace

\subsection{Programming}
Java \textbullet{} Python \textbullet{} Bash \textbullet{} Spring Boot

\sectionspace

\subsection{Messaging}
Kafka \textbullet{} JMS \textbullet{} MQ \textbullet{} SQS \textbullet{} SNS

\sectionspace

\subsection{Databases}
Oracle \textbullet{} PostgreSQL \textbullet{} MySQL \textbullet{} MongoDB \textbullet{} Cassandra \textbullet{} DynamoDB

\sectionspace

\subsection{Monitoring}
CloudWatch \textbullet{} Grafana \textbullet{} Prometheus \textbullet{} ELK \textbullet{} Splunk \textbullet{} Dynatrace

\sectionspace

\subsection{Operating Systems}
Linux \textbullet{} Unix \textbullet{} Windows


\sectionspace % Some whitespace after the section
%------------------------------------------------
% Links
%------------------------------------------------

\section{Links} 

LinkedIn: linkedin.com/in/ramkotni \\


\sectionspace % Some whitespace after the section

%----------------------------------------------------------------------------------------

\end{minipage} % The end of the left column
\hfill
%
%----------------------------------------------------------------------------------------
%	RIGHT COLUMN
%----------------------------------------------------------------------------------------
%
\begin{minipage}[t]{0.66\textwidth} % The right column takes up 66% of the text width of the page

%------------------------------------------------
% Experience
%------------------------------------------------
\section{Experience}

\runsubsection{ERCOT}
\descript{| Senior Cloud Platform Engineer}
\location{Apr 2025 – Present | Taylor, TX}
\begin{tightitemize}
\sectionspace
\item Engineer and automate cloud/on-prem platforms using Terraform, Ansible, and Kubernetes.
\item Manage CI/CD pipelines and cloud-native services supporting critical energy systems.
\item Implement monitoring and incident response with CloudWatch, Grafana, and Prometheus.
\item Support Kafka-based microservices and improve platform reliability and scalability.
\end{tightitemize}

\sectionspace

\runsubsection{Amazon Robotics}
\descript{| Senior Cloud Infrastructure Engineer}
\location{Feb 2023 – Mar 2025 | North Reading, MA}
\begin{tightitemize}
\item Designed AWS infrastructure for large-scale microservices and robotics platforms.
\item Built Terraform IaC and managed ECS/Fargate container workloads.
\item Developed CI/CD pipelines using Jenkins and AWS native services.
\item Improved system performance through monitoring, logging, and cost optimization.
\end{tightitemize}

\sectionspace

\runsubsection{Biogen}
\descript{| Cloud Infrastructure Lead}
\location{Jun 2022 – Jan 2023 | Durham, NC}
\begin{tightitemize}
\item Led AWS cloud migration and infrastructure modernization initiatives.
\item Automated infrastructure with Terraform and built CI/CD pipelines.
\item Supported Kubernetes deployments and cloud security/compliance requirements.
\end{tightitemize}

\sectionspace

\runsubsection{Dell Technologies}
\descript{| Application Architect / DevOps Lead}
\location{Jul 2015 – May 2022 | Austin, TX}
\begin{tightitemize}
\item Designed and delivered cloud-based microservices using Java, Spring Boot, and AWS.
\item Led migration from monolithic systems to scalable cloud architectures.
\item Built CI/CD pipelines, automated deployments, and API integrations.
\item Worked with Kafka, REST APIs, and cloud‑native DevOps tooling.
\end{tightitemize}

\sectionspace

\runsubsection{IBM}
\descript{| Senior Infrastructure Engineer}
\location{May 2012 – Jul 2015 | New York, US}
\begin{tightitemize}
\item Managed Linux enterprise infrastructure and automated operational workflows.
\item Implemented monitoring, automation, and disaster recovery solutions.
\item Supported Oracle and DB2 databases and middleware platforms.
\end{tightitemize}

\sectionspace

\runsubsection{Innominds \& Wells Fargo}
\descript{| Software Engineer / Infrastructure Engineer}
\location{Dec 2009 – Mar 2012 | San Jose, CA \& Nov 2007 – May 2009 |Desmoines, IA}
\begin{tightitemize}
\item Developed Java/J2EE enterprise applications and automation tools.
\item Supported CI/CD, deployments, and infrastructure operations.
\item Worked with Linux, databases, and enterprise integration technologies.
\end{tightitemize}


%------------------------------------------------
% Awards
%------------------------------------------------

\sectionspace % Some whitespace after the section

%------------------------------------------------
% Societies
%------------------------------------------------

%\section{Membership} 

%\begin{tabular}{rll}
%2011-2015 & Alpha Kappa Lambda Fraternity\\

%\end{tabular}

%\sectionspace % Some whitespace after the section

%----------------------------------------------------------------------------------------

\end{minipage} % The end of the right column

%----------------------------------------------------------------------------------------
%	SECOND PAGE (EXAMPLE)
%----------------------------------------------------------------------------------------

%\newpage % Start a new page

%\begin{minipage}[t]{0.33\textwidth} % The left column takes up 33% of the text width of the page

%\section{Example Section}

%\end{minipage} % The end of the left column
%\hfill
%\begin{minipage}[t]{0.66\textwidth} % The right column takes up 66% of the text width of the page

%\section{Example Section 2}

%\end{minipage} % The end of the right column

%----------------------------------------------------------------------------------------

\end{document}